---
title: "Nobel Laureates Lab"
author: "Team Name"
date: today
format: 
    gfm: 
      toc: true
      toc-depth: 2
      fig-height: 4
      fig-width: 9
editor: visual
execute: 
  echo: true
  warning: false
---

```{r}
#| label: setup
#| include: false
# This chunk loads packages and Nobel data silently
library(tidyverse)
nobel <- read_csv("data/nobel.csv")
```

Use this template to write up your answers to Exercises 1 through 6 in the Nobel Laureates Lab instructions.

## Exercise 1

```{r}
#|label: first_ex

```

Remove this text, and add your answer for Exercise 1 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.

### Exercise 2

Remove this text, and add your answer for Exercise 2 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.

```{r}
#|label: ex2

```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.

```{r}
#|label: ex3

```

### Exercise 4

```{r}
#|label: ex4

```

### Exercise 5

```{r}
#|label: ex5

```

### Exercise 6

```{r}
#|label: ex6

```
